% Ubah judul dan label berikut sesuai dengan yang diinginkan.
\section{Conclusion}
\label{sec:kesimpulan}

% Ubah paragraf-paragraf pada bagian ini sesuai dengan yang diinginkan.
Based on the test results conducted throughout the execution of this final project, the following are the findings:

\begin{enumerate}

  \item The lowest average delay time was found in the test by sending a string with 1 value transmitted via WiFi. The average delay time is 0.03499708571 seconds.

  \item The highest average delay time was found in the test by sending a string with 2 values transmitted via WiFi. The average delay time is 1.059681387 seconds.
  
  \item Additional delay time in the data sender program is required for several tests. This is done to prevent data flooding that can disrupt the performance of ESP32.

  \item Some tests require additional delay time in the data sender program, such as sending a String containing 2 values via Bluetooth, requiring an additional delay time of 1.5 seconds, sending JSON data with 2 values via Bluetooth, requiring an additional delay time of 1.1 seconds, sending a String containing 2 values via WiFi, requiring an additional delay time of 1.3 seconds, sending JSON data with 2 values via WiFi, requiring an additional delay time of 1.5 seconds, sending JSON data with 1 value via Bluetooth, requiring an additional delay time of 1 second, and sending JSON data with 1 value via WiFi, requiring an additional delay time of 1.5 seconds.
  
  \item Only 2 tests do not require additional delay time in the data sender program, namely sending a String with 1 value via Bluetooth and sending a String with 1 value via WiFi. 
  
  \item Data transmitted to control the wheelchair via computer vision is better using a String with only 1 value, namely the direction variable analogized with 1 character. 
  
  \item Data transmission used to control the wheelchair via computer vision is better using WiFi with ESP32 as its Access Point.

\end{enumerate}

\section{Recommendation}
\label{chap:saran}

Based on the results obtained from this research, the suggestions that can be considered for further development are as follows:

\begin{enumerate}

  \item The rotation speed of the motor is controlled through the ESP32 using a button or a potentiometer.

  \item Trying to use other gestures to control the movement of the wheelchair.

\end{enumerate}
